Figures

### 2019-06-26 code/figures.rmd
Added tau vs. effect size correlation per effect type (SMD, fisher's z)

@@

OR_fit <- function(x){ #fit rma to odds raios
  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
  hetero <- confint(fit)$random[c(1, 3), ] 
  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}

fit_OR <- dat %>% 
  filter(effect %in% OR2d) %>% 
  split(.$effect) %>% 
  map_dfr(OR_fit, .id = "effect")

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference",
                              'Raw mean difference' = "Mean Difference",
                              'Risk difference' = "Risk Difference",
                              'r' = "Correlation")) %>% 
  left_join(tau2_per_type) %>% 
  filter(!effect %in% OR2d) %>% #drop old SMD converted OR
  bind_rows(fit_OR) %>% #and instead add OR meta-analyzed as OR
  mutate(effect_type = ifelse(is.na(effect_type), "Odds Ratio", effect_type),
         eff_size = abs(eff_size)) #need the absolute values for plotting

@@

tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_line(stat = "smooth", method = "lm", se = FALSE, color = "black", alpha = .5, linetype = "dashed") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, scales = "free") #use free scales since scales are different

>>>>

MD_fit <- function(x){
    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])
}

fisher_fit <- function(x){
    fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])
    }

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(effect_type == "Raw mean difference" & !outcomes1_2 == "mean _ SE") %>% #No method in metafor to compute SMD when standard deviations not given, so skip this study 
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect")

fisher <- dat %>% 
  filter(effect_type == "r") %>% 
  split(.$effect) %>% 
  map_dfr(fisher_fit, .id = "effect")

@@

#If we don't use the Odds ratios we don't need the below
# OR_fit <- function(x){ #fit rma to odds raios
#   fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
#   hetero <- confint(fit)$random[c(1, 3), ] 
#   data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
#              s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
#              tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}
# 
# fit_OR <- dat %>% 
#   filter(effect %in% OR2d) %>% 
#   split(.$effect) %>% 
#   map_dfr(OR_fit, .id = "effect")

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% 
  filter(!effect %in% c(OR2d, MD_standardized$effect, fisher$effect)) %>% #drop old SMD converted OR, unstandardized MD and raw correlations
  bind_rows(MD_standardized) %>% 
  bind_rows(fisher) %>% 
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% fisher$effect, "Fisher's z", effect_type),
         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
  filter(effect_type %in% c("Standardized Mean Difference", "Fisher's z"))

@@

tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different
